---
title: "Customising the models to compare"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customising the models to compare}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(metaUI)
```

## Adding, editing and removing models

You might wish to show different models. For now, the easiest way to do that is to save the app into a folder, as shown in the vignette("getting_started"). Then open models.R to edit the models.

## Removing models

To remove models, you can add a comment (`#`) in front of the line where it is *first* defined in upper part of the file where `models_to_run` are defined ... and ignore the longer part in the `models_code` below. So to remove the Trim-and-fill model, you simply need to add the `#` shown below - or alternatively to delete that line.

```{r eval=FALSE}
   "Robust Variance Estimation",                      FALSE,       "as.numeric(mod$reg_table$b.r)",      ... 
#   "Trim-and-fill",                                   TRUE,        "mod$TE.random",                     ...
   "P-uniform star",                                  TRUE,        "mod$est",                            ...  
```

## Add or edit models

To add or edit models, you need to understand a bit more about the structure of the file. If contains two parts - firstly, the `models_to_run` which has the names of the models and the details on how to extract summary data, and then the `models_code` that contains the code to estimate them.

For `models_to_run`, you need to provide the following details for each model:

- `name` of the model to be displayed
- `aggregated` TRUE/FALSE value whether it needs to be estimated with the dataset aggregated by sample (i.e. without dependent effect sizes)

And then code within "" that allows you to export the following from the model object, called `mod`:

- `es`: the effect size
- `LCL` & `UCL`: the lower and upper bounds of the 95% confidence intervals for the effect size
-  `k`: the model-specific count (state whether effects, studies, or imputed effects)

For `models_code`, you need to provide code, again in "", that estimates the model based on fields available in the dataset produced by `prepare_data()` (for models where `aggregated = FALSE`) or aggregated by `metaUI_aggregate()` in the generated `analysis.R`. Aggregation retains the first row’s metadata but does not infer aggregate p-values or N; do not interpret retained metadata as a new scientific aggregation rule.

If your model code is complicated, it might be worthwhile to create helper functions to call from within the `models_code` entry. Add them above the final `models_to_run` expression in `models.R`, e.g., `my_meta_fun <- function(...)`. The app sources model code in its own environment. Declare and install any extra dependencies yourself; the default manifest does not infer them. Custom models must return the declared fitting scale. `NA` intervals are allowed only when explicitly specified; failed fits are reported.

The default multilevel and RVE specifications call helpers in the generated
`analysis.R`. Study-level aggregation also happens there through `metaUI_aggregate`;
`df_agg` is exposed by the server but does not infer N or p-values. Editing those
helpers requires restarting the app. `generate_shiny(overwrite=TRUE)` replaces
all generated files, including `analysis.R`; build into a fresh folder and compare
changes to preserve hand edits. It never clears unrelated files from the folder.

Custom models default to `options=list(fit_cache_entries=0)`. Only explicitly
opt deterministic code into a 1–3-entry session cache. Random models or code that
reads external state must leave it disabled. A cache hit preserves the original
fit times, warnings, and status, and is disclosed as `cache_hit`.
